Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-23 article/article.tex
(+) partitions + transitions

\subsection{workload}

@@

The Monte Carlo Tree search algorithm maximize a objective function. This function
represent a potential reward over a path, i.e.\ a list of partitions over time.
Given the loss function defined previously, the target function can be
construct as:
\begin{equation}
  \psi(\pi) = \frac{1}{f(\pi)}
\end{equation}

>>>>

\subsubsection{Partitions}

In the configuration problem, the airspace needs to be devided into sectors. Each
sector represent a area controlled by two officers and is composed of
one or more elementary modules. A partition $P$ is a set of
sectors covering all the airspace.

\subsubsection{Transitions}

During the day, and with the evolution of the trafic, the workload (rigorously
defined in \ref{sub:workload}) vary. To help controllers to maintain a
homogeneous level of workload, the airspace partitioning needs to be adapt
and therefore make transition from an inital partition to a target partition.
This maneuver requires coordination hence increase controller's workload.
This is the reason why a full reconfiguration isn't doable in practice, and
only a selection of transitions can be operate.

In our model, three transistions are possible namely a merge, a transfer
and a split. For an airspace composed of three modules $A$, $B$, and $C$,
those actions represent:
\begin{itemize}
  \item merge: $\{\{A, B\}, \{C\}\} \quad \rightarrow \quad \{\{A, B, C\}\}$ 
  \item split: $\{\{A, B, C\}\} \quad \rightarrow \quad \{\{A, B\}, \{C\}\}$ 
  \item transfer: $\{\{A, B\}, \{C\}\} \quad \rightarrow \quad \{\{A\}, \{B, C\}\}$ 
\end{itemize}

\subsection{Workload}\label{sub:workload}

@@

The Monte Carlo Tree search algorithm maximize a objective function. This function
represent the reward of a path, i.e.\ a list of partitions over time.
Given the loss function defined previously, the target function can be
construct as:
\begin{equation}
  Q(\pi) = \frac{1}{f(\pi)}
\end{equation}
